\begin{thebibliography}{99}
\bibitem{Knuth}Donald E.\ Knuth, Don Kunuth's Home Page. 
\url{https://www-cs-faculty.stanford.edu/~knuth/}（参照\today）.

\bibitem{JIS}``JIS X 4051: 2004 日本語文書の組版方法,'' 日本産業規格, 2004. 
\url{https://kikakurui.com/x4/X4051-2004-02.html}（参照\today）.

\bibitem{typst}モリサワ公式note, ``多言語組版ルールブック,'' 株式会社モリサワ, 2024. 
\url{https://www.morisawa.co.jp/fonts/multilingual/typesetting/}（参照\today）.

\bibitem{PDF}``PDF Reference, version 1.7 (6th Ed.),'' Adobe Systems Inc., Oct.\ 2006. 
\url{https://opensource.adobe.com/dc-acrobat-sdk-docs/pdfstandards/pdfreference1.7old.pdf}（参照\today）.

\bibitem{PS}``アドビポストスクリプト技術へのおさそい,'' アドビ株式会社, 1998. 
\url{https://www.adobe.com/jp/print/postscript/pdfs/welcmps2.pdf}（参照\today）.

\bibitem{latex}The {\LaTeX} Project, {\LaTeX} -- A document preparation system, 2024.
\url{https://www.latex-project.org/}（参照\today）.

\bibitem{ptex}アスキードワンゴ編集部, ``ASCII Nihongo {\TeX} (Publishing {\TeX}),'' 株式会社ドワンゴ, 2002. 
\url{https://asciidwango.github.io/ptex/}（参照\today）.

\bibitem{unicode} ``Unicode\textregistered 16.0.0.'' Unicode Inc., Sept.\ 2024. 
\url{https://www.unicode.org/versions/Unicode16.0.0/}（参照\today）.

\bibitem{opntyp} ``OpenType\textregistered,'' Adobe Systems Inc., 2023. 
\url{https://www.adobe.com/jp/products/type/opentype.html}（参照\today）.

\bibitem{uptex}Takuji Tanaka, ``up{\TeX}, up{\LaTeX} -- 内部Unicode版 p{\TeX}, p{\LaTeX}の実装,'' TeXメモ, Nov.\ 2021. 
\url{http://www.t-lab.opal.ne.jp/tex/uptex.html}（参照\today）.

\bibitem{luatex}The LuaTex team, Lua{\TeX}, 2024. 
\url{https://www.luatex.org}（参照\today）.

\bibitem{luatexj}Hironori Kitagawa, ``luatexja -- Typeset Japanese with Lua(La)\TeX,'' Comprehensive {\TeX} Archive Network (CTAN), Oct.\ 2024. 
\url{https://ctan.org/pkg/luatexja}（参照\today）.

\bibitem{mactex} ``Mac{\TeX},'' {\TeX} Users Group, Mar. 2024. 
\url{https://www.tug.org/mactex/}（参照\today）.

\bibitem{homebrew} R\'{e}mi Pr\'{e}vost, Mike McQuaid, and Danielle Lalonde, Homebrew -- The Missing Package Manager for macOS (or Linux), 2024.
\url{https://brew.sh}（参照\today）.

\bibitem{macports} The MacPorts Project, The MacPorts Project Official Homepage, 2024.
\url{https://www.macports.org}（参照\today）.

\bibitem{cm}Donald E.\ Knuth, ``Computer Modern Font,'' Font Squirrel, Feb. 2017. 
\url{https://www.fontsquirrel.com/fonts/computer-modern}（参照\today）.

\bibitem{harano}Masamichi Hosoda, ``原ノ味フォント/Harano Aji Fonts,'' GitHub, Oct. 2023.
\url{https://github.com/trueroad/HaranoAjiFonts}（参照\today）.

\bibitem{jscls}Haruhiko Okumura, ``jsclasses -- Classes tailored for use with Japanese,'' Comprehensive {\TeX} Archive Network (CTAN), Feb.\ 2023.
\url{https://ctan.org/pkg/jsclasses}（参照\today）.

\bibitem{jlw3c}千葉弘幸, 枝本順三郎, Richard Ishida, 石野恵一郎, 加藤誠一, 小林龍生, 小林敏, Nathaniel McCully, 小野澤賢三, Felix Sasaki, 下農淳司, 塩澤元, 薛富僑, ``日本語組版処理の要件（日本語版）,'' World Wide Web Consortium (W3C) Working Group, Aug.\ 2020.
\url{https://www.w3.org/TR/jlreq/}（参照\today）.

\bibitem{jlreq}Noriyuki Abe, jlreq, Feb.\ 2024.
\url{https://tug.org/docs/latex/jlreq/jlreq-ja.html}（参照\today）.

\bibitem{jlreq-deluxe} Yukimasa Morimi, ``jlreq-deluxe -- Multi-weight Japanese font support for the jlreq class,'' Comprehensive {\TeX} Archive Network (CTAN), Feb.\ 2024.
\url{https://ctan.org/pkg/jlreq-deluxe}（参照\today）.

\bibitem{OTF}Takuji Tanaka, ``japanese-otf -- Advanced font selection for platex and its friends,'' Comprehensive {\TeX} Archive Network (CTAN), Oct.\ 2023.
\url{https://ctan.org/pkg/japanese-otf}（参照\today）.

\bibitem{pxchfon} Takayuki Yato, ``pxchfon – Japanese font setup for p\LaTeX and up\LaTeX,''  Comprehensive {\TeX} Archive Network (CTAN), Aug.\ 2023.
\url{https://ctan.org/pkg/pxchfon}（参照\today）.

\bibitem{fontenc}The {\LaTeX} Project Team, ``fontenc -- Standard package for selecting font encodings,'' Comprehensive {\TeX} Archive Network (CTAN), Nov.\ 2024.
\url{https://ctan.org/pkg/fontenc}（参照\today）.

\bibitem{stix2}David M.\ Jones, ``stix2-otf -- OpenType Unicode text and maths fonts,'' Comprehensive {\TeX} Archive Network (CTAN), Apr.\ 2021.
\url{https://ctan.org/pkg/stix2-otf/}（参照\today）.

\bibitem{roboto} Bob Tennent, ``roboto -- Support for the Roboto family of fonts,'' Comprehensive {\TeX} Archive Network (CTAN), Sept.\ 2022.
\url{https://ctan.org/pkg/roboto}（参照\today）.

\bibitem{mathtools} Morten Høgholm, Lars Madsen, and the {\LaTeX}3 project, ``mathtools -- Mathematical tools to use with amsmath,'' Comprehensive {\TeX} Archive Network (CTAN), Oct.\ 2024.
\url{https://ctan.org/pkg/mathtools}（参照\today）.

\bibitem{graphicx} David Carlisle, and The {\LaTeX} Project Team, ``graphicx -- Enhanced support for graphics,'' Comprehensive {\TeX} Archive Network (CTAN), Sept.\ 2021.
\url{https://ctan.org/pkg/graphicx}（参照\today）.

\bibitem{xcolor}The {\LaTeX} Project Team, ``xcolor -- Driver-independent color extensions for \LaTeX and pdf{\LaTeX},'' Comprehensive {\TeX} Archive Network (CTAN), Nov.\ 2023.
\url{https://ctan.org/pkg/xcolor}（参照\today）.

\bibitem{pxrubrica}Takayuki Yato, ``pxrubrica -- Ruby annotations according to JIS X 4051,'' Comprehensive {\TeX} Archive Network (CTAN), Apr.\ 2017.
\url{https://ctan.org/pkg/pxrubrica}（参照\today）.

\bibitem{ascmac}Japanese {\TeX} Development Community, ``ascmac -- Boxes and picture macros with Japanese vertical writing support,'' Comprehensive {\TeX} Archive Network (CTAN), Jan.\ 2020.
\url{https://ctan.org/pkg/ascmac}（参照\today）.

\bibitem{tcolorbox}Thomas F.\ Sturm, ``tcolorbox --Coloured boxes, for \LaTeX examples and theorems, etc,'' Comprehensive {\TeX} Archive Network (CTAN), Oct.\ 2024.
\url{https://ctan.org/pkg/tcolorbox}（参照\today）.

\bibitem{listings}Jobst Hoffmann, ``listings -- Typeset source code listings using {\LaTeX},'' Comprehensive {\TeX} Archive Network (CTAN), Sept.\ 2024.
\url{https://ctan.org/pkg/listings}（参照\today）.

\bibitem{hyperref}The {\LaTeX} Project Team, ``hyperref -- Extensive support for hypertext in {\LaTeX},'' Comprehensive {\TeX} Archive Network (CTAN), Sept.\ 2024.
\url{https://ctan.org/pkg/hyperref}（参照\today）.

\bibitem{pxjahyper}Takayuki Yato, ``pxjahyper -- Hyperref support for p{\LaTeX},'' Comprehensive {\TeX} Archive Network (CTAN), Apr.\ 2022.
\url{https://ctan.org/pkg/pxjahyper}（参照\today）.

\bibitem{PXex} Takayuki Yato, ``PXchfon-extras,'' GitHub, Oct.\ 2019.
\url{https://github.com/zr-tex8r/PXchfon-extras/tree/master}（参照\today）.

\bibitem{tlcontrib}Norbert Preining, tlcontrib -- supplementary TeX Live package repository, 2024. 
\url{https://contrib.texlive.info}（参照\today）.
\end{thebibliography}